Predicting the Housing Market using \\ Linear Regression

### 2023-11-12 manuscript/Manuscript.tex
added more discussion
added linear regression model

@@

% A summary, again, of the contributions of the research.
% The research question posed as the `need’ of the introduction must be answered here (Zeiger 2000).
% Limitations of the current study
One limitation of this current study is that this data set is very small and has very limited variables. The next step for this study is to gain access to a data set from the actual house market and produce a model with it. 
% Future directions.
In the last decade, there have been three recessions in the United States. Being able to create a stronger model that can precisely predict the market can be more beneficial than just looking at house prices. If the model can see the fluctuation in the market, then the model can also help predict when the next recession is going to hit.

>>>>

\begin{figure}[h!]
    \caption{Linear Regression Plot}
    \includegraphics[width=1\textwidth]{linear_regression_plot.pdf}
    \label{fig:regression_plot}
\end{figure}
Figure~\ref{fig:regression_plot} shows a linear regression plot with the predicted house price against the actual house price. Based on this plot that was created, it looks like the model was somewhat accuracy in predicting the prices.

@@

% A summary, again, of the contributions of the research.
% The research question posed as the `need’ of the introduction must be answered here (Zeiger 2000).
% Limitations of the current study
One limitation of this current study is that this data set is very small and has very limited variables. The next step for this study is to gain access to a data set from the actual house market and produce a model with it. Another factor that can limit this study is that nowadays, there are infinite numbers of factors that can affect the cost of a house. So creating a model to include all these new factors is practically impossible. 
\\
\smallskip

% Future directions.
In the last decade, there have been three recessions in the United States. Being able to create a stronger model that can precisely predict the market can be more beneficial than just looking at house prices. If the model can see the fluctuation in the market, then the model can also help predict when the next recession is going to hit.
